---
title: "My Fancy Presentation"
author: "Andrew Derbak"
date: "January 13, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## My New Slde
Some content on it

***
```{r, echo=TRUE, fig.align='center'}
plot( y = mtcars$weight, x = mtcars$mpg)
```

A slide without a title

## Another new slide
### A Top-Level Subheading
#### A second level subheading

- Bullet one
- Bullet two

1. Item a
2. Item b

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

